### 2020-08-11 thesis/thesis.tex
fix indent

\SetAcknowledgeText{
For providing vital guidance and parts of the code, I thank Dr. Bronwyn Rayfield. For providing help with computing resources parts of the code, I thank Dr. Guillaume Larocque. For providing advice on STSIM implementation and code, I thank Dr. Colin Daniel and Dr. Leonardo Frid. I thank Dr. Guillaume Larocque and Dr. Yann Boulanger for their help in providing the LANDIS outputs and editorial help for the associated appendix. \\
I thank all students, staff and organizations involved in the design and realisation of the workshop. I thank Aurélie Sierra for her invaluable guidance and counsel. I thank all students and staff facilitators: Madeleine Gauthier, Mikayla Salmon-Beitel and Violette Bertrand. I thank Geneviève Poirier and Mariève Lafontaine for their participation in the design, planning and organization of the workshop. I also thank Renée Gagnon for her precious help securing a location for the workshop. \\
For providing essential funding for this project, I thank the Fonds de recherche du Québec – Nature et technologies (FRQNT). For providing logistical support I thank Dr. Helen Elina and Mr. Philippe Auzel. \\
For providing key information on land use data, I thank Martin Joly, Marie-Josée Côté and Benoit Jobin. \\
I thank my supervisor, Prof. Andrew Gonzalez, for his support and for believing in my abilities every step of the way. I also thank members of my committee, Prof. Brian Leung and Prof. Elena Bennett for their timely and wise council at every committee meeting. I thank all my fellow grad students and especially Alex Arkilanian for all the help revising proposals, discussion ideas, and providing key support. \\
I thank Laura, Philippe, and Talia for their unwavering support. Thank you to Blanka and Peter for sheltering me and putting up with my writing process during the thick of the pandemic. \\
}%
\Acknowledge%

>>>>

\SetAcknowledgeText{
For providing vital guidance and parts of the code, I thank Dr. Bronwyn Rayfield. For providing help with computing resources parts of the code, I thank Dr. Guillaume Larocque. For providing advice on STSIM implementation and code, I thank Dr. Colin Daniel and Dr. Leonardo Frid. I thank Dr. Guillaume Larocque and Dr. Yann Boulanger for their help in providing the LANDIS outputs and editorial help for the associated appendix. \\
\indent I thank all students, staff and organizations involved in the design and realisation of the workshop. I thank Aurélie Sierra for her invaluable guidance and counsel. I thank all students and staff facilitators: Madeleine Gauthier, Mikayla Salmon-Beitel and Violette Bertrand. I thank Geneviève Poirier and Mariève Lafontaine for their participation in the design, planning and organization of the workshop. I also thank Renée Gagnon for her precious help securing a location for the workshop. 
\indent For providing essential funding for this project, I thank the Fonds de recherche du Québec – Nature et technologies (FRQNT). For providing logistical support I thank Dr. Helen Elina and Mr. Philippe Auzel. \\
\indent For providing key information on land use data, I thank Martin Joly, Marie-Josée Côté and Benoit Jobin. \\
\indent I thank my supervisor, Prof. Andrew Gonzalez, for his support and for believing in my abilities every step of the way. I also thank members of my committee, Prof. Brian Leung and Prof. Elena Bennett for their timely and wise council at every committee meeting. I thank all my fellow grad students and especially Alex Arkilanian for all the help revising proposals, discussion ideas, and providing key support. \\
\indent I thank my mother Laura, my father Philippe, and Talia for their unwavering support. Thank you to Blanka and Peter for sheltering me and putting up with my writing process during the thick of the pandemic. \\
}%
\Acknowledge%
